Computer Science House Constitution

### 2019-11-03 constitution.tex
Add a missing 'and' to conditional description
Correct single room ties

\asubsubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
The member with top priority is the member with on-floor status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation. Each Active Member with On-Floor Status who passes the Membership Evaluation is granted one (1) Housing Priority Point.
\\* \\*
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
\asubsubsubsection{Single Room Assignments}
When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
This process continues until a member selects to move into the single room.
Once in a single room, a House member retains the assignment until voluntarily giving it up.
It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
\asubsubsubsection{Double Rooms as Single rooms}
During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
This only applies if there is a totally vacant room.

>>>>

\asubsubsection{Housing Priority System}
The Housing Priority System is a means for determining the priority a House member has in a Housing issue such as Single Room Assignment or the Assignment of Available Housing.
The member with top priority is the member with on-floor status and the most Housing Priority Points.
Housing Priority Points are accumulated once per Operating Session at the conclusion of the Membership Evaluation. Each Active Member with On-Floor Status who passes the Membership Evaluation is granted two (2) Housing Priority Points.
\\* \\*
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
\asubsubsubsection{Single Room Assignments}
When a single room on the House becomes available it is offered to the member who carries the highest Housing Priority as defined in \ref{Housing Priority System}.
In the event of a tie, the members will be approached simultaneously and if they are unable to decide fairly between themselves, the assignment of priority will be made by random selection of the tied members.
If that House member declines the option, it will be offered to the member with the next highest Housing Priority.
This process continues until a member selects to move into the single room.
Once in a single room, a House member retains the assignment until voluntarily giving it up.
It should be noted that members selecting this option must agree to any additional charges applied by the Department of Residence Life for residing in a single room.
\asubsubsubsection{Double Rooms as Single rooms}
During the third week of each semester, if there is no waiting list for residency on the House, any vacant rooms will be offered to House members as single rooms assignments according to the method as described in \ref{Single Room Assignments}.
It should be noted that this does not mean members will be relocated into empty spaces so that the member with top priority is offered the single.
This only applies if there is a totally vacant room.
